---
title: "DairyHerdData: commonly available datasets in cattle dairy herds."
output: 
  github_document:
    toc: true
    toc_depth: 1
---

This package gathers 4 example datasets that are commonly available in cattle dairy herds. These datasets can be used to teach herd data analysis and to develop and test epidemiological indicators. 

The 4 datasets are:

- `rec`: milk recording data for 100 herds
- `ai`: artificial insemination data
- `mvt`: movements of animals between herds (birth, commercial transactions, deaths)
- `anim`: individual animal information such as date and herd of birth, breed...

The datasets were constructed by first taking a random sample of 100 dairy herds enrolled in a milk recording scheme between 2006 and 2010. Constraints were however placed on the number of animals recorded and the number of cows recorded per test-day. The data from the cows in this initial dataset were then retrieved from the artificial insemination, movement and animal databases. All the herd and animal data were then anonymised.


# Package installation

The package is only available from github. In order to install it, use the `install_github()` function from the `devtools` package.

```{r install-package}
#| eval: false

devtools::install_github("AurMad/DairyHerdData")
```

# Documentation

The datasets are documented. For example, in order to know what is in the `rec` dataset, just type `?rec` in your console after having attached the package.

```{r help-rec}
#| eval: false

## attaching the package
library(DairyHerdData)

## help page for the rec dataset
?rec
```


# Loading the data

To load any of these dataset in memory, save it in a new variable after having attached the package. This will create a `data.frame` containing the data.

```{r loading-rec}
## attaching the package
library(DairyHerdData)

## loading the milk recording dataset
rec <- rec

## inspecting the data
head(rec)
```

